Numerous variables relating to 2016 election in 2021 US GSS

### 2022-03-18 outputs/paper/paper.Rmd
ggplot
adeded age data

```{r}
library(ggplot2)
reduced_data %>%
  ggplot(aes(x = gender, fill = pres16)) +
  geom_bar()

>>>>

```{r}
library(ggplot2)
reduced_data %>%
  ggplot(aes(x = age)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = gender)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = race)) +
  geom_bar()

reduced_data %>%
  ggplot(aes(x = gender, fill = pres16)) +
  geom_bar()
